WWTF Grant Proposal\\Leveraging Resolution for Verified Program Synthesis

### 2022-03-28 WWTF/Draft Alexander/Proposal.tex
Reorganized sections
wording

	We now give details on (WP1). As mentioned in the previous section there are currently two main approaches in the literature for obtaining programs from classical proofs: 1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation. However, since non-intuitionistic tautologies like $\neg\forall xP(x)\to \exists x\neg P(x)$ or $A\vee \neg A$ are assigned a program, we lose the realizability of $\exists$ and $\vee$. As discussed in~\cite{practical}, in practice it is often possible to eliminate the non-intuitionistic fragments. We aim to establish stronger theoretical guarantees on when this is possible but also more practical benchmarks on the feasibility of this approach, even when realizability is not ensured by a theorem. 2) Sometimes classical validity guarantees intuitionistic validity, most famously for $\Pi_2$-formulas in Arithmetic~\cite{Friedman}. There have been various generalizations of this result, most notably by Schwichtenberg's group~\cite{schwichtenberg}. We will adapt their work to our more general setting.

>>>>

	We now give details on (WP1). We will consider two approaches from the literature for obtaining programs from classical proofs: 1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation. However, since non-intuitionistic tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ are assigned a program, we lose the realizability of $\exists$ and $\vee$. As discussed in~\cite{practical}, in practice it is often possible to eliminate the non-intuitionistic fragments. We aim to establish stronger theoretical guarantees on when this is possible but also more practical benchmarks on the feasibility of this approach, even when realizability is not ensured by a theorem. 2) Sometimes classical validity guarantees intuitionistic validity, most famously for $\Pi_2$-formulas in Arithmetic~\cite{Friedman}. There have been various variations of this result, most notably by Schwichtenberg's group~\cite{schwichtenberg}. We will adapt their work to our more general setting.
